\documentclass[letterpaper,12pt]{article}
\usepackage{hyperref}
\usepackage{fullpage}
\urlstyle{same}
\author{David A Timm}
\title{Resume}
\setcounter{secnumdepth}{-1}
\begin{document}
\pagenumbering{gobble}
\begin{center}
\section{David A Timm}

E: \href{mailto:timmmeister@gmail.com?subject=You%27re%20hired!}
{\nolinkurl{timmmeister@gmail.com}}
T: \mbox{(303) 652-7177}
\end{center}

\begin{center}
\subsection{Technical Skills}
\end{center}

\begin{itemize}
\item Learning new things quickly (I learned \LaTeX{} just for this!)
\item C/C++, C\textsuperscript{{$\sharp$}}.NET, Python, Java, Perl, GNU tools
\item General problem isolation and troubleshooting (I'm awesome at this)
\item Desktop wired and wireless support
\item Dell laptop and desktop hardware replacement
\item Active Directory administration/Directory Services API
\item Windows, Mac OS X, Linux, Android and iOS
\end{itemize}

\begin{center}
\subsection{Experience}
\end{center}

\begin{flushleft}
\textbf{Site Visit Tech}: 05/13--Present Denver Public Schools
\textbf{Denver, CO}
\end{flushleft}

I roam from town to town, helping those in need\ldots{} I support schools in the
deployment, use, and repair of any technology a student may lay their hands on.
Smart boards, computers of all stripes, clickers, nComputing, printers, and
even a few electric pencil sharpeners. 

\begin{flushleft}
\textbf{Hotline Tech II}: 05/11--05/13 Denver Public Schools \textbf{Denver, CO}
\end{flushleft}

I was first/second line tech support for staff of Denver Public Schools.
Financial and HR software, wireless connections, Mac, PC, all that fun stuff.
My record for tickets processed in a day still stands at 232.

\begin{flushleft}
\textbf{Student}: 02/10--04/11 Colorado School of Trades \textbf{Lakewood, CO}
\end{flushleft}

Gunsmithing? Really!? I spent fourteen months completing a program that
encompassed troubleshooting, repairing, and building (from blueprints or to
purpose) parts for firearms. It has helped my ability to visualize problems
and directly taught me a lot of very interesting skills. There were many
resources available to students to complete their work, and as a student, I
was expected to take advantage of them. The curriculum takes students through
basic fabrication, machining, woodworking, and design/function courses,
covering special tools and techniques as they apply to the trade. I completed
the program with a 3.3 GPA.

\newpage
\begin{flushleft}
\textbf{Associate Systems Admin}: 02/08---10/09 Dish Network
\textbf{Littleton, CO}
\end{flushleft}

Four technicians supported all access requests across the Dish Network
enterprise. Billing software, Active Directory, UNIX accounts, VPN, and more
all came to us. We also handled all requests to terminate this access, and
while I was at Dish Network, I developed a C\textsuperscript{{$\sharp$}}.NET
application that automatically took the output of the HR system and used it to
find and terminate access across Active Directory and several other
applications. I also oversaw the conversion of Dish's VPN to a two-factor
certificate authentication and assisted in deploying it.

\begin{flushleft}
\textbf{RMA support tech}: 09/07--10/07 Bolder Staffing \textbf{Boulder, CO}
\end{flushleft}

All software troubleshooting for Polycom IP phones went through our desk. When
it was unresolvable, we gave the customer an RMA number and processed a
replacement.

\begin{flushleft}
\textbf{Tech Support Analyst}: 04/2007--06/2007 TEK Systems 
\textbf{Lafayette, CO}
\end{flushleft}

We supported payroll and CAD software for Northrup Grumman contractors all over
the world, from the Baghdad green zone to the shipyards of Pascagoula, MS.

\begin{flushleft}
\textbf{Tech Support Analyst}: 05/06--08/07 CCI, Inc. \textbf{Boulder, CO}
\end{flushleft}

Along with a team of thirty other technicians, I supported Cisco Systems
employees with nearly every aspect of computer support. In-depth
troubleshooting of Microsoft products, VPN software, networking, and several
proprietary tools all fell under our jurisdiction. I was consistently atop
(or close) the list of agent performance metrics by call time, resolution rate,
calls handled, and customer satisfaction. I trained several new agents while
I worked there, and I helped to develop numerous support documents for future
use.
\end{document}
